### 2021-08-06 src/cover-letter.tex
Version as submitted.

    Many thanks for considering our manuscript for possible publication in
    \textit{Nature Human Behavior}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership.

    We incorporate detailed NPIs, different tests, and vaccinations in an agent-based
    model. Importantly, we do so in a way that allows to calibrate its parameters based
    on routinely available data. We apply the model to the second and third waves of the
    CoViD-19 pandemic in Germany over a period of 9 months, achieving a good fit to
    actual infection rates.

    Our core substantive result is that rapid testing has been very effective relative
    to many NPIs in a low-medium vaccination environment.

>>>>

    Many thanks for considering our manuscript for possible publication in
    \textit{Nature Human Behavior}. Our hope is that modelling the evolution of the
    CoViD-19 pandemic and the relative effectiveness of diverse interventions are of
    interest to a broad readership. On way to view the manuscript is as taking the same
    basic approach as the work by Aleta et al.---published a year ago in this
    journal---and demonstrating its usefulness for modelling and understanding the
    spread of the virus under different policies.

    We incorporate detailed NPIs, different tests, and vaccinations in an agent-based
    model, taking into account behavioural reactions to symptoms or positive test
    results. Importantly, we do so in a way that allows to calibrate its parameters
    based on routinely available data. We apply the model to the second and third waves
    of the CoViD-19 pandemic in Germany over a period of 9 months, achieving a good fit
    to actual infection rates.

    Our core substantive result is that rapid testing has been very effective relative
    to many NPIs in a low-medium vaccination environment. This is the relevant scenario
    for most countries across the world at present; it seems also applicable to countries
    with high vaccination rates under the conditions of the delta variant.
